---
title: "Check a correlated model"
author: "Robin Donatello"
format: html
execute: 
  warning: false
  message: false
  echo: false
---

# Purpose
To see if a hierarchical model allowing for the correlation of student reponses within sector is appropriate. 

```{r, include=FALSE}
library(mice)
library(lme4)
#library(effectsize)
#library(tidymodels)

# Non-imputed data (bns, bns_unfiltered)
source(here::here("Statewide Analysis/data_management.R"))


# Load Imputed Data
imp_bns_clean_mids_unfiltered <- readRDS(here::here("Statewide Analysis/imp_bns_clean_mids_unfiltered.RData"))


# Each data set will have slightly different n counts due to filtering, hence, the following steps need to be taken to filter each data set separately and pool the results later

# 1) Create five different data sets from the unfiltered mids
# 2) Filter Each Data Set and create .imp variable
for (i in 1:5) {
data <- imp_bns_clean_mids_unfiltered %>% 
  complete(action = i) %>%
  filter(units >= 12,
        (calfresh_eligible == 1 | calfresh == "CalFresh"), 
        (gender== "Men" | gender == "Women")
        ) %>%
  mutate(.imp = i)

assign(paste0("data_",i),data,.GlobalEnv)

}

# 3) Create a list of the 5 data sets.This will be used to fit a glm on each data set.
data_list <- list(data_1, data_2, data_3, data_4, data_5)

```

Final model: `glm(food_insecure_2item ~ calfresh + gender + age + eth_hispanic + units + school_grouped + firstgen, data = data_list[[i]], family = binomial)`

# Fit multilevel model

Only going to check this on 1-2 of the imputed data sets. If a high ICC is observed and decision is made to go with a HLM then proper analysis post imputation will be used. 

```{r}
for (i in seq_along(data_list)) {
  test <- glmer(food_insecure_2item ~ calfresh + gender + age + eth_hispanic + 
                  units + firstgen + (1|school_grouped), 
                  data = data_list[[i]], family = "binomial", 
                  control = glmerControl(optimizer = "bobyqa"))
  summary(test)
}
```

4 out of 5 data sets have a boundary/convergence issue. 

```{r}
glmer1 <- glmer(food_insecure_2item ~ calfresh + gender + age + eth_hispanic + 
                units + firstgen + (1|school_grouped), 
                data = data_1, family = "binomial", 
                control = glmerControl(optimizer = "bobyqa"))
summary(glmer1)
VarCorr(glmer1)
sjPlot::tab_model(glmer1, show.r2=FALSE)
```

ICC and random intercept variance super close to 0. 
Compare coefficient results. 

```{r}
glm.1 <- glm(food_insecure_2item ~ calfresh + gender + age + eth_hispanic + 
                units + firstgen + school_grouped, 
                data = data_1, family = "binomial")
sjPlot::tab_model(glm.1, show.r2=FALSE)
```


Decision: A correlated model is not needed. Increased complexity of the model not warranted, no meaningful change in coefficients or large enough ICC. 

## SNAP vs academic success

```{r}
sac.glm <- glm(course_activities ~ calfresh + gender + age + eth_hispanic + units + school_grouped + food_insecure_2item + firstgen, 
               family = binomial(link = "logit"), data = data_2)

sac.glmer <- glmer(course_activities ~ calfresh + gender + age +
                     eth_hispanic + units  + food_insecure_2item +
                     firstgen + (1|school_grouped), 
               data = data_2, family = "binomial", 
               control = glmerControl(optimizer = "bobyqa"))
```

```{r}
#| layout-ncol: 2
sjPlot::tab_model(sac.glm, show.r2=FALSE)
sjPlot::tab_model(sac.glmer, show.r2=FALSE)
```

Same decision. 




